\thetitle

### 2020-11-19 writing/discussion.tex
Add rough outline of discussion points

\begin{itemize}
  \item Interesting discoveries...?

  \item Comparison of existing GT systems represented in our study.  
    Natural is here, transient is here, erasure is here, and they
        compare as...

>>>>

\begin{itemize}
  \item Any kind of dynamic checking has a large positive impact, whether blame or stacktraces are used.
    \begin{itemize}
    \item Both in terms of usefulness and programmer effort
    \item Erasure extremely often fails to provide any helpful information.
    \item That said, there are no long trails for Erasure.
    \end{itemize}

  \item Blame helps significantly over just using stacktraces for both Natural and Transient.
    \begin{itemize}
    \item Natural's blame improves over exceptions by nearly 20\%
    \item Transient's blame improves over exceptions half as much
    \end{itemize}

  \item Natural clearly offers the most utility, but Transient is not too far behind.
    \begin{itemize}
    \item Natural clearly improves over all other modes
    \item Transient improves significantly over all other modes except Natural.
    \item Keep in mind that our selection of scenarios is biased toward Erasure & Transient.
    \end{itemize}

  \item Discussion of how confidence / margin of error should be interpreted wrt these results?
